
\chapter{Samenwerking}
\label{sec:samenwerking}

De samenwerking tijdens de ontwikkeling van Triump verliep vlekkeloos. Er werd geluisterd naar de inbreng van ieder groepslid en steeds werd iedereen betrokken bij het nemen van een beslissing. Bij het uitvoeren van een project van deze omvang is het belangrijk dat elk groepslid hetzelfde doel voor ogen houdt. Daarom werd meermaals per week samengezeten om de vooruitgang te evalueren en de taken te herverdelen. Door de vele fysieke bijeenkomsten wist elk lid wat zijn taken waren en waarmee de andere leden bezig waren. Hierdoor werden divergerende ideeën tussen projectleden snel opgemerkt.

%Zoals af te leiden uit figuur \ref{fig:planning_uiteindelijk} in %de bijlagen werden de taken gelijk verdeeld over de groepsleden. %Aangezien elk groepslid zijn verantwooordelijk nam  \\

\textbf{Ik heb geen idee wat ik nog kan schrijven, vandaar deze inspirerende quotes:}

\begin{itemize}
\item
"Individual commitment to a group effort--that is what makes a team work, a company work, a society work, a civilization work." --Vince Lombardi
\item
"Talent wins games, but teamwork and intelligence win championships." --Michael Jordan
\item
"Teamwork is the ability to work together toward a common vision. The ability to direct individual accomplishments toward organizational objectives. It is the fuel that allows common people to attain uncommon results." --Andrew Carnegie
\item
"Alone we can do so little, together we can do so much." --Helen Keller
\item
"Remember, teamwork begins by building trust. And the only way to do that is to overcome our need for invulnerability." --Patrick Lencioni
\item
"I invite everyone to choose forgiveness rather than division, teamwork over personal ambition." --Jean-Francois Cope
\item
"None of us is as smart as all of us." --Ken Blanchard
\item
"Coming together is a beginning. Keeping together is progress. Working together is success." --Henry Ford
\item
"If everyone is moving forward together, then success takes care of itself." --Henry Ford
\item
"The strength of the team is each individual member. The strength of each member is the team." --Phil Jackson
\item
"Collaboration allows teachers to capture each other's fund of collective intelligence." --Mike Schmoker
\item
"It takes two flints to make a fire." --Louisa May Alcott
\item
"Unity is strength. . . when there is teamwork and collaboration, wonderful things can be achieved." --Mattie Stepanek
\item
"To me, teamwork is the beauty of our sport, where you have five acting as one. You become selfless." --Mike Krzyzewski
\item
"The best teamwork comes from men who are working independently toward one goal in unison." --James Cash Penney
\end{itemize}